---
title: "miRetrieve"
subtitle: "microRNA text mining in PubMed abstracts"
author: Julian Friedrich<sup>1,2</sup>, Hans-Peter Hammes<sup>2</sup>, Guido Krenning<sup>1</sup> <br> <br> <font size="2"> <sup>1</sup>Cardiovascular Regenerative Medicine (CAVAREM), Department of Pathology and Medical Biology, University Medical Center Groningen, University of Groningen, The Netherlands. <br> <sup>2</sup>Section of Endocrinology, 5th Medical Department, Medical Faculty of Mannheim, University of Heidelberg, Mannheim, Germany. </font>
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_document
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cerulean
link-citations: true
bibliography: miretrieve.bib
csl: elsevier-vancouver.csl
vignette: >
  %\VignetteIndexEntry{miRetrieve_pkg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r noidea, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE, echo=FALSE}
path <- "/Users/Julian/Documents/Jupyter/miRetrieve_pkg_files/"

require("knitr")
knitr::opts_knit$set(base.dir = path, base.url = path, root.dir = path)
library(kableExtra)
library(magrittr)
library(dplyr)
library(ggplot2)
```

```{r imagespath, include=FALSE, echo=FALSE, eval=TRUE}
tokenization_img <- "Tokenization_miRetrieve_res.png"
stopword_img <- "Stopwordremoval_miRetrieve_res.png"
lda_img <- "LDA_miRetrieve_resized.png"
```

# Introduction

miRetrieve is an R package designed to facilitate text mining with microRNAs (miRNAs) 
in PubMed abstracts. By extracting miRNA names from large amounts of text, miRetrieve 
is able to provide insights into thousands of articles within a short amount of time.

In this vignette, we describe how to use miRetrieve. 
First, we are going to illustrate the mechanisms underlying miRetrieve by introducing 
basic tools of text analysis, which is a part of *Natural Language 
Processing* (NLP). Next, we are going to explain how to use the functions in miRetrieve, 
before applying miRetrieve in a case study.

# Natural Language Processing

**Natural Language Processing (NLP)** describes the application of computational
methods to process and analyze language^[https://www.lexico.com/en/definition/natural_language_processing].  

In this section, we are going to present common tools in NLP, namely *tokenization*,
*tf-idf*, *stop word removal*, and *topic modeling*. These tools aid in gaining
and extracting insights from a collection of texts, which are contained in a 
**corpus**.  
While the list presented here is not exhaustive, it illustrates the mechanisms
underlying many functions in miRetrieve and shall facilitate their use.  

## Tokenization

**Tokenization** refers to splitting text into smaller pieces, called *tokens*.   

While text can be tokenized in many different ways, two common approaches are 
**single word tokenization** and **n-gram tokenization** (Fig. \@ref(fig:tokenize)).  
Whereas single word tokenization splits text into single words (Fig. \@ref(fig:tokenize)
**A**), n-gram tokenization
splits text into each combination of *n* adjacent words, which are referred to
as *2-grams*, *3-grams* etc. (Fig. \@ref(fig:tokenize) **B**).  
During tokenization, capital letters are transformed 
into lower case letters and punctuation such as **.** , **,** , or **-** is 
substituted with a space, if not specified otherwise. As a result, terms such as 
*T1DM* are transformed into *t1dm*, while compound terms such as *low-density* are 
tokenized into *low* and *density*.  

```{r tokenize, echo=FALSE, fig.cap="<font size='1'><b>Tokenization in NLP.</b> Tokenization refers to splitting text into smaller pieces, called tokens. Two common tokenization approaches are single word tokenization <b>(A)</b> and n-gram tokenization, splitting text into each combination of n adjacent words such as 2-grams <b>(B)</b></font>."}
knitr::include_graphics(tokenization_img)
```
  
</br>
After a text is tokenized, determining the frequency of each token can provide 
first insights into the overall subject of the text. If *inflammation* is one
of the most frequent tokens in a text, it can be assumed that 
*inflammation* partially describes the topic of the text, too. Furthermore, 
comparing token frequency between texts can be a good starting point
to determine text similarity.  
  
While single word tokenization facilitates text comparison, n-grams are prone to
impede direct comparison due to their complexity. To meaningfully compare the token
frequency of the 2-gram *low grade* between texts, for example, requires
many texts to have the exact same combination of *low* and *grade* multiple times, 
whereas it is clear that the chance of same word combinations 
decreases with increasing n-gram size.  

However, n-grams are preferred to single words when
word context matters. Single word tokenization of *Low grade inflammation*
(*low*, *grade*, *inflammation*) loses the context of *low*, and it is not
clear if *low* is used in the context of *low grade inflammation*, *low expression*,
or even *low-density lipoprotein*. After tokenizing *Low grade inflammation* into 2-grams,
however, the resulting token *low grade* hints that *low* is neither associated 
with *expression* nor with *low-density lipoprotein*, which provides more insight
into the context of *low* than single word tokenization alone.

When a function depends on tokenization in miRetrieve, such as `plot_mir_terms()` or
`compare_mir_terms()`, the tokenization type
can often be regulated via the `token` argument. `token = "words"` performs
single word tokenization, while `token = "ngrams"` and a specified
`n` argument performs n-gram tokenization.

```{r tokenizeexample, eval = FALSE}
# Analyze miRNA-term association of miR-34 by single word tokenization
plot_mir_terms(df,
               mir = "miR-34",
               token = "words")

# Analyze miRNA-term association of miR-34 by 2-gram tokenization
plot_mir_terms(df,
               mir = "miR-34",
               token = "ngrams",
               n = 2)
```

## tf-idf 

**term frequency–inverse document frequency**, or **tf-idf** in short, 
determines how unique and important a token is to one text compared to other texts.  

Instead of comparing raw token frequency between texts, 
tokens are "weighed" depending on how often they are mentioned in
one text compared to all other texts under investigation.  
When tokenizing the texts

  * *Cancer can affect any organ.* 
  * *Cancer can be caused by mutations.* 
  * *Cancer can be caused by viruses*
  
into single words, the tokens *cancer* and *can* are present
in all three texts, while the tokens *be*, *caused*, and *by* are
present in two out of three texts. The tokens *affect*, *any*, *organ*,
*mutations*, and *viruses*, however, are only present in one text compared to 
all other texts. Taken together, this suggests that the tokens *cancer* and *can* 
offer no information when distinguishing these texts,
while the text specific tokens *organ*, *mutations*, and *viruses* make the texts
distinguishable and are thus more important for each text.  

In miRetrieve, tf-idf can be used to determine how important a term 
is to a miRNA compared to all other miRNAs in a corpus. If *inflammation* is 
only associated with miR-146, but not associated with miR-374 or
miR-23, then *inflammation* is very specific for miR-146 in the given corpus.  
When a miRetrieve function offers tf-idf analysis, such as `plot_mir_terms()`,
`compare_mir_terms()`, or `plot_wordcloud()`, it can be applied by 
setting `tf.idf = TRUE`. 
  
```{r tfidfexample, eval = FALSE}
# Analyze miRNA-term association of miR-34 with tf-idf
plot_mir_terms(df,
               mir = "miR-34",
               tf.idf = TRUE)

# Analyze miRNA-term association of miR-34 without tf-idf
plot_mir_terms(df,
               mir = "miR-34",
               tf.idf = FALSE)
```
  
## Stop words

**Stop words** refer to common words that offer no 
information for text analysis,
such as *a*, *is*, or *whether*, which is why stop words are often removed in text 
analysis (Fig. \@ref(fig:stop)).  

```{r stop, echo=FALSE, fig.cap="<font size='1'><b>Stop word removal.</b> Stop words refer to common words that offer no information for text analysis. It is therefore common practice to remove stop words in text analysis.</font>"}
knitr::include_graphics(stopword_img)
```

<br>
In miRetrieve, stop words can be removed in two ways depending on tokenization
type, namely stop word removal for single word tokenization and stop word removal for
n-gram tokenization.  

### Stop words for single word tokenization

To remove stop words for single word tokenization, stop words must 
be provided in a data frame. miRetrieve comes with two predefined stop words data
frames, namely `stop_words` from the **tidytext** package, and `stopwords_miretrieve`, 
a data frame manually curated for PubMed abstracts. While `tidytext::stop_words` 
removes the most common English words such as *a*, *is*, or *whether*, `stopwords_miretrieve` removes common
words of PubMed abstracts, such as *western*, *qpcr*, or *significant*. 

```{r stopwordremoval, eval = FALSE}
# Remove common English words with `stop_words` from tidytext
plot_mir_terms(df,
               mir = "miR-34",
               stopwords = tidytext::stop_words)

# Remove common PubMed terms with `stopwords_miretrieve` from miRetrieve
plot_mir_terms(df,
               mir = "miR-34",
               stopwords = stopwords_miretrieve)
```
    
`stop_words` and `stopwords_miretrieve` can be combined with `combine_stopwords()`
to remove English and PubMed stop words simultaneously.
  
```{r combinestopwords, eval = FALSE}
# Combine stop words from tidytext and miRetrieve
stopwords_large <- combine_stopwords(tidytext::stop_words,
                                     stopwords_miretrieve)

# Remove English PubMed stop words
plot_mir_terms(df,
               mir = "miR-34",
               stopwords = stopwords_large)
```
  
Additionally, stop words can be generated from custom terms with `generate_stopwords()`.
These generated stop words can be added 
to an existing stop word data frame using `combine_with`.

```{r customstop, eval = FALSE}
# Vector of custom stop words
custom_stopwords <- c("these", "are", "some", "custom", "stop", "words")

# Generate custom stop words data frame
# Combine custom stop words with `stopwords_miretrieve`
custom_stopwords_df <- generate_stopwords(custom_stopwords,
                                          combine_with = stopwords_miretrieve)
```
   
   
### Stop words for n-gram tokenization
  
For n-gram tokenization, miRetrieve removes only English stop words. 
As the quality of n-grams depends on word context, removing too
many words might distort the results and is thus not recommended.  
If a function offers n-gram tokenization, stop words can be removed by
setting `stopwords_ngram = TRUE`.^[The stop words removed for n-gram tokenization are based on `tidytext::stop_words`[@tidytext].]

```{r stoptwogram, eval = FALSE}
# Remove English stop words for 2-gram tokenization
plot_mir_terms(df,
               mir = "miR-34",
               token = "ngrams",
               n = 2,
               stopwords_ngram = TRUE)
```

## Topic modeling

**topic modeling** describes the identification of topics 
in a corpus. Topics can either be identified in a supervised, e.g. 
controlled manner, or in an unsupervised, e.g. blind manner.  

### Supervised topic modeling

**Supervised topic modeling** refers to identifying known topics in a corpus, 
and thus requires prior knowledge.  

miRetrieve offers supervised topic modeling by heuristically identifying
topics with keywords: First, a topic is defined by keywords, and these keywords are
then used to calculate a *topic score* for each text in the corpus. The topic score 
reflects how well a text matches the keywords, and if the topic score surpasses a 
threshold, the text is considered to match the topic.  

There are three pre-implemented heuristic topic models in miRetrieve, namely  

* abstracts that investigate miRNAs in patients,
* abstracts that investigate miRNAs in animal models,
* abstracts that investigate miRNAs as biomarkers.

While knowledge about how often a miRNA has been investigated in patients or in animal
models can estimate the translation between bench and bedside, identifying 
which miRNA is most likely a biomarker aids in estimating its specificity compared
to other fields.  

For each heuristic model, a topic score can be calculated using 
`calculate_score_patients()`, `calculate_score_animals()`,
and `calculate_score_biomarker()`. Furthermore, each `calculate_score_*()` function
has a corresponding `plot_score_*()` function (`plot_score_patients()`, 
`plot_score_animals()`, and `plot_score_biomarkers()`), which
plots the distribution of scores across all abstracts, and helps in choosing
a threshold for topic assignment.

```{r plotscore, eval = FALSE}
# Plot score distribution, determine threshold
plot_score_patients(df)

# Calculate score for abstracts investigating miRNAs in patients
calculate_score_patients(df,
                         threshold = 5)
```

Next to the pre-implemented models, custom topics can be defined with custom keywords 
using `calculate_score_topic()` and its corresponding `plot_score_topic()` function.

```{r customscore, eval = FALSE}
# Define keywords of custom topic "angiogenesis"
keywords_angiogenesis <- c("angiogenesis", "vegf", "vascularization",
                           "sprouting")

# Plot distribution of "angiogenesis" scores
plot_score_topic(df,
                 keywords = keywords_angiogenesis,
                 name.topic = "Angiogenesis")

# Calculate angiogenesis score for each abstract
df_angio <- calculate_score_topic(df,
                                  keywords = keywords_angiogenesis,
                                  threshold = 3)
```

While one abstract can belong to multiple topics, abstracts
can also be assigned to only one out of two or more topics: 
First, topic scores for all topics of interest are calculated, using 
`calculate_score_topic()`. Afterwards, each abstract is assigned to the topic
where it surpasses a threshold and achieves the highest topic score,  
using `assign_topic()`. If the topic score of an abstract does not surpass
the threshold in any topic, the topic of the abstract is labelled as `"Unknown"`.

```{r assigntopic, eval = FALSE}
# Define keywords for type 1 diabetes
keywords_t1dm <- c("pancreas", "beta cells", "gada")

# Define keywords for type 2 diabetes
keywords_t2dm <- c("insulin resistance", "obesity", "metformin")

# Calculate type 1 diabetes scores for each abstract
df_diabetes <- calculate_score_topic(df,
                                     keywords = keywords_t1dm,
                                     name.topic = "T1DM")

# Calculate type 2 diabetes scores for each abstract
df_diabetes <- calculate_score_topic(df_diabetes,
                                     keywords = keywords_t2dm,
                                     name.topic = "T2DM")

# Assign abstracts with a score of >= 3 in "T1DM" to type 1 diabetes
# Assign abstracts with a score of >= 3 in "T2DM" to type 2 diabetes
# Abstracts with a score < 3 in "T1DM" and "T2DM" are assigned to
# "Unknown".
assign_topic(df_diabetes,
             col.topic = c("T1DM", "T2DM"),
             threshold = c(3, 3))
```

### Unsupervised topic modeling

**Unsupervised topic modeling** refers to identifying topics in a corpus with 
algorithms. As unsupervised topic modeling does not require prior knowledge, 
unsupervised topic modeling can be used to detect and uncover hidden topics in a corpus.  

In miRetrieve, unsupervised topic modeling can be conducted with the Latent Dirichlet 
Algorithm (LDA), based on the **topicmodels** package[@topicmodels].  

To perform topic modeling with LDA, LDA requires the user to specify the number
of topics. Based on different criteria and probability distributions, LDA 
then identifies as many topics as specified in the corpus, and assigns each text in the corpus a 
*topic probability* to belong to either topic. Ultimately, each text is assigned to the topic
with its highest topic probability (Fig. \@ref(fig:lda) **A**).  
Based on the texts within each topic, the subjects
of the unsupervisedly identified topics can then be determined by comparing their 
token frequency (Fig. \@ref(fig:lda) **B**).  

```{r lda, echo=FALSE, fig.cap="<font size='1'><b>Unsupervised topic modeling with LDA.</b> <b>(A)</b> LDA is fit on a corpus and identifies k = 3 topics based on different criteria. For each text in the corpus, a topic probability to belong to either topic is calculated and the text is assigned to the topic with the highest topic probability. <br> <b>(B)</b> Tokenizing the texts in a topic and determining their most frequent tokens aids in inferring the main subject of unsupervisedly discovered topics.</font>"}
knitr::include_graphics(lda_img)
```

<br>
The whole process of identifying topics and calculating topic probabilities is
referred to as *model fitting*. While an LDA model can be fit with `fit_lda()`,
the topics are ultimately assigned to each text with `assign_topic_lda()`. The 
subjects of the topics can be identified with `plot_lda_terms()`.

```{r fitlda, eval = FALSE}
# Fit LDA model with k = 4 topics
# Identify 4 topics in df
lda_model <- fit_lda(df,
                     k = 4)

# Identify subject of topics
plot_lda_term(lda_model)

# Assign LDA topics
assign_topic_lda(df,
                 lda_model = lda_model,
                 topic.names = c("Topic1", "Topic2", "Topic3", "Topic4"))
```

As the optimal number of topics for LDA modeling is often unknown,
one approach is to fit many LDA models, which differ in topic number, and to compare 
their *perplexity* (Fig. \@ref(fig:perplexfig)). In LDA, perplexity measures how well a model fits
the topics, while a lower perplexity corresponds to a better model. When comparing the
perplexity of LDA models with different topic numbers, an increase in topic number
often leads to a steep decrease in model perplexity at the beginning,
indicating a model improvement with an increase in topic number. After a certain
point, however, further increasing the topic number often leads to a marginal
decrease in perplexity only, indicating that the model improves only marginally with
an increase in topic number. The topic number where the decrease in perplexity 
starts to flatten is usually a good starting point for LDA modeling in practice.

```{r perplexfig, echo=FALSE, fig.cap="<font size='1'><b>Perplexity 'elbow' plot comparing the perplexity of LDA models over a range of topic numbers.</b><br>Fitting LDA models over k = 2, k = 3, and k = 4 topics considerably decreases the perplexity. Fitting LDA models over further k = 5, k = 6, and k = 7 topics, however, decreases the perplexity only slightly, indicating a marginal model improvement with k > 4. This suggests k = 4 topics as a  practical starting point to explore LDA topic modeling in this corpus.</font>"}
perplex_value <- c(2000, 1800, 1600, 1550, 1500, 1450)

perplexity <- dplyr::tibble("Perplexity" = perplex_value,
                            "Topics" = seq(2, length(perplex_value) + 1))

ggplot2::ggplot(perplexity, aes(Topics, Perplexity)) + 
    ggplot2::geom_point(color = "#188CDF") + 
    ggplot2::geom_line(color = "#188CDF") + 
    ggplot2::theme_classic() +
    ggplot2::xlab("Number of topics k")
```

In miRetrieve, the perplexity of different LDA models can be compared with
`plot_perplexity()`. `plot_perplexity()` fits LDA models over different
topic numbers and compares their perplexity in an *elbow plot*.

```{r perplexityplotexplanation, eval = FALSE}
# Plot perplexity for 2 to 5 topics
# Identify optimal topic number
plot_perplexity(df, start = 2, end = 5)
```

# miRetrieve functions

In the following section, we are going to describe how to use and combine the
functions in miRetrieve.  

First, we are going to outline how to load, prepare,
and save for and from analysis. Afterwards, we are going to explain how to analyze the
miRNA landscape in one subject, before describing how to compare the miRNA
landscape of multiple subjects.

## Load, prepare, and save data

### Load data

miRetrieve is optimized to work with PubMed abstracts in MEDLINE or xml-format, 
which can be downloaded from PubMed via "Send to" --> "File" --> 
"Format: MEDLINE/xml" --> "Create File".  

The resulting MEDLINE/.xml-file can be loaded into R with either `read_pubmed_medline()` 
or `read_pubmed_xml()` respectively. As `read_pubmed_medline()` is faster than 
`read_pubmed_xml()`, it is recommended to use MEDLINE-files.  

When loading abstracts with `read_pubmed_*()`, all abstracts can be assigned a `Topic` column, which denotes the subject of a file and facilitates miRNA comparison
between topics. If a `Topic` column is not specified while loading, it 
can also be added with `add_col_topic()`.

```{r loaddata, eval = FALSE}
# Read in MEDLINE-file from diabetes abstracts
# Denote abstracts as "Diabetes"
df <- read_pubmed_medline("medlinefile_diabetes.txt", topic = "Diabetes")

# Is the same as
df <- read_pubmed_medline("medlinefile_diabetes.txt")
df <- add_col_topic(df, topic.name = "Diabetes")
```

Multiple files can be combined into one data frame with `combine_df()`,
which is crucial when comparing miRNAs of multiple topics.

```{r combinedata, eval = FALSE}
# Load first MEDLINE-file
df1 <- read_pubmed_medline("medlinefile1.txt",
                           topic = "cANCA")

# Load second MEDLINE-file
df2 <- read_pubmed_medline("medlinefile2.txt",
                           topic = "pANCA")

# Combine df1 and df2
df_large <- combine_df(df1, df2)
```

### Prepare data

#### Subset abstracts

Abstracts loaded into R can be subset for original research or review articles 
with `subset_research()` and `subset_review()` respectively. Furthermore, abstracts can 
also be subset for a specific publishing period with `subset_year()`.  
Subsetting abstracts with `subset_*()` keeps only abstracts of interest,
while abstracts belonging to another article type or published outside the 
defined period are dropped.

```{r subsetresearch, eval = FALSE}
# Subset for abstracts of original research articles
df_research <- subset_research(df)
```

#### Extract miRNA names

One of the core functions of miRetrieve the extraction of miRNA names from
abstracts with `extract_mir_df()`. Extracted miRNA names are stored in a separate 
`miRNA` column, where each miRNA name occupies one row.

Next to extracting miRNA names from abstracts, miRNA names can also be
extracted from single strings with `extract_mir_string()`.  

Both `extract_mir_*()` functions extract miRNA names either without or with
a possible trailing letter (e.g. *miR-23* or *miR-23a*). As the use of miRNA nomenclature is
rather inconsistent throughout literature, it is recommended to ignore trailing
letters with `extract_letters = FALSE`.

```{r extractmir, eval = FALSE}
# Extract miRNA names from a data frame without trailing letters
extract_mir_df(df,
               extract_letters = FALSE)

# Extract miRNA names from a string with trailing letters
extract_mir_string("miR-146a is an important miRNA in inflammation.",
                   extract_letters = TRUE)
```

#### Subset and indicate miRNA names

After extracting miRNA names, abstracts can be subset for miRNAs with 
`subset_mir()` and `subset_mir_threshold()`.  
While `subset_mir()` subsets abstracts for specified miRNAs,
`subset_mir_threshold()` subsets abstracts for miRNAs that are mentioned
with a determined frequency. This frequency can either be an integer,
corresponding to the minimal number of abstracts a miRNA is mentioned in, 
or it can be a decimal between 0 and 1, corresponding to the minimal relative number of
abstracts a miRNA is mentioned in.

```{r subsetmir, eval = FALSE}
# Keep only abstracts with miR-126 and miR-146
df_mir126_miR_146 <- subset_mir(df,
                                mir.retain = c("miR-126", "miR-146"))

# Keep only abstracts with miRNAs mentioned in at least 5% of all abstracts
df_five_ab <- subset_mir_threshold(df,
                                   threshold = 0.05)
```

Instead of subsetting abstracts for a specific miRNA, 
abstracts with a specific miRNA can also be labelled with 
`indicate_mir()`. Per specified miRNA name in `indicate_mir()`, a separate *Yes/No* column
is added indicating the presence of the miRNA in the abstract.

```{r indicatemir, eval = FALSE}
# Indicate abstracts with miR-126 and miR-146
df_mir126_miR_146 <- indicate_mir(df,
                                  indicate.mir = c("miR-126", "miR-146"))

# Save data frame as an .xlsx file
# Filter for miR-126 and miR-146 in excel
save_excel(df_mir126_miR_146,
           excel_file = "df_mir_126146.xlsx")
```

#### Subset data frame

While many functions of the `subset_*()` and `indicate_*()` family
provide the possibility of subsetting a data frame, each 
data frame can also be individually subset with `subset_df()`.  
`subset_df()` is a wrapper of **dplyr**'s `filter()`.

```{r, eval = FALSE}
# Subset data frame with customized arguments
subset_df(df,
          col.filter = miRNA,
          filter_for = "miR-126")

# `subset_df()` is a more general version of
subset_mir(df, "miR-126")
```

### Save data

During analysis, any data frame or graph can be saved locally with 
`save_excel()` or `save_plot()` respectively.  

#### Save data frame to excel

`save_excel()` saves a data frame as an .xlsx-file. When more
than one data frame is passed to `save_excel()`, each data frame is saved as a 
separate work sheet in the same .xlsx-file.

```{r, eval = FALSE}
# Save df1 and df2 to the same .xlsx-file
save_excel(df1, df2,
           excel_file = "miRetrieve_df.xlsx")
```

#### Save plots

`save_plot()` saves the last generated plot, while the plot properties can be
defined with `width`, `height`, and `dpi`.
`save_plot()` is a wrapper of **ggplot2**'s `ggsave()`.

```{r, eval = FALSE}
# Save last plot
save_plot("Last_plot.pdf",
          height = 5,
          width = 7,
          dpi = 300)
```

### Extract PubMed-IDs

PubMed-IDs can be extracted from a data frame with `get_pmid()`. By default,
`get_pmid()` copies the PubMed-IDs to the clipboard, which can be used further
outside R.  
Additionally, `get_pmid()` can also extract PubMed-IDs as a string 
by setting `copy = FALSE`.

```{r, eval = FALSE}
# Copy PubMed-IDs to clipboard
get_pmid(df,
         copy = TRUE)
```


## miRNA text mining in one subject

The following section focuses on miRNA text mining in one subject,
opposed to miRNA text mining in several subjects.  

Here, we are going to describe how to count miRNAs and display
their development. Next, we are going to explain how to display which terms a miRNA is 
associated with, before illustrating how to visualize which targets miRNAs regulate. 

The functions in this section require the miRNAs names to be extracted with 
`extract_mir_*()`.  

### Count miRNAs

How many abstracts mention a miRNA can be identified either with 
`count_mir()` or `plot_mir_count()`. While `count_mir()` displays the miRNA count
in a data frame, `plot_mir_count()` visualizes the count of the most
frequently mentioned miRNAs.

```{r, eval = FALSE}
# Count how many abstracts mention a miRNA
count_mir(df)

# Plot the count of the five most frequently mentioned miRNAs
plot_mir_count(df,
               top = 5)
```

### Count exceeding miRNAs

Next to counting how many abstracts mention one miRNA, counting how many miRNAs 
are mentioned in a minimal number of abstracts can be done with 
`count_mir_threshold()` or `plot_mir_count_threshold()`.  

Counting how many miRNAs are mentioned in a minimal number of abstracts provides
information if the majority of abstracts focus on a few miRNAs only, or if 
the interest in several miRNAs is evenly distributed across a field.  

`count_mir_threshold()` accepts a `threshold` argument and counts how many
miRNAs are mentioned in at least `threshold` abstracts. `threshold` can either be
an integer, counting how many miRNAs are mentioned in a minimal number of
abstracts, or it can be a decimal between 0 and 1, counting how many miRNAs are 
mentioned in a relative number of abstracts compared to all abstracts.  

`plot_mir_count_threshold()` displays the count of miRNAs over several thresholds. 
Similar to `count_mir_threshold`, the thresholds can
either be integers or decimals. 

```{r, eval = FALSE}
# Count how many miRNAs are mentioned in at least 5 abstracts
count_mir_threshold(df,
                    threshold = 5)

# Plot how many miRNAs are mentioned in at least 5 to 10 abstracts
plot_mir_count_threshold(df,
                         start = 5,
                         end = 10)
```

### Count miRNAs per year

How often a miRNA was mentioned per year can be visualized with `plot_mir_development()`.

```{r, eval = FALSE}
# Plot development of miR-126 and miR-146
plot_mir_development(df,
                     mir = c("miR-126", "miR-146"))
```

### Count new miRNAs per year

How many miRNAs are mentioned for the first time in a year can be displayed with 
`plot_mir_new()`.  

Displaying how many miRNAs are mentioned for the first time in a year estimates the 
dynamism of a field, e.g. if recent abstracts mention miRNAs previously 
not reported, or if recent abstracts focus on miRNAs already mentioned in previous years.  

`plot_mir_new()` also provides a `threshold` argument determining
in how many abstracts of a year a miRNA must be mentioned to be considered *mentioned*. 
By setting a `threshold`, miRNAs that are only sparsely mentioned in
a year are ignored.

```{r, eval = FALSE}
# Plot newly mentioned miRNAs per year
# miRNAs need to be reported in at least 3 abstracts/year
# to be considered "mentioned"
plot_mir_new(df,
             threshold = 3)
```

### Associate miRNAs with terms

Terms often associated with a miRNA can be visualized using `plot_mir_terms()`.  

While `plot_mir_terms()` performs single word tokenization
by default, `plot_mir_terms()` can also perform n-gram tokenization
by setting `token  = ngrams` and specifying a separate `n` argument.

```{r, eval = FALSE}
# Plot top terms of miR-126
plot_mir_terms(df,
               mir = "miR-126")

# Plot top 2-grams of miR-126
plot_mir_terms(df,
               mir = "miR-126",
               token = "ngrams",
               n = 2)
```

Next to plotting the top terms as a bar plot, top terms can also be visualized
as a word cloud with `plot_wordcloud()`.^[`plot_wordcloud()` is based on the **wordcloud** package[@wordcloud].]

```{r, eval = FALSE}
# Word cloud of miR-126
plot_wordcloud(df,
               mir = "miR-126")
```

### Indicate terms

Abstracts can be screened for terms with `indicate_term()`. Per term,
`indicate_term()` signals it presence in an abstract with a separate *Yes/No* 
column.  

How often a term must be in an abstract to be considered *present* 
can be controlled with a `threshold` argument. Furthermore, `indicate_term()`  can 
also keep only abstracts containing the term(s) of interest via the
`discard` argument. A possible application is to keep abstracts that mention
a certain drug, and to re-count the most frequent miRNAs in this subset.

```{r, eval = FALSE}
# Indicate and keep abstracts that mention "metformin" at least twice
abstracts_metformin <- indicate_term(df,
                                     term = "metformin",
                                     threshold = 2,
                                     discard = TRUE)

# Count miRNAs in "metformin" abstracts
count_mir(abstracts_metformin)
```

### Identify miRNA targets

miRetrieve can integrate miRNA targets from excel files such as *miRTarBase*[@mirtarbase] with 
`join_targets()`.  

`join_targets()` loads an excel-file with PubMed-IDs and miRNA targets and adds it to
a miRetrieve data frame by matching their PubMed-IDs.

```{r, eval = FALSE}
# Adds targets from miRTarBase (see "References") to df
df_targets <- join_targets(df,
                           excel_file ="miRTarBase_MTI.xlsx",
                           col.pmid.excel = "References (PMID)",
                           col.target.excel = "Target Gene",
                           col.mir.excel = "miRNA")
```

After adding the targets, target frequency can be counted with
`count_target()` or visualized with `plot_target_count()`. 

```{r, eval = FALSE}
# Count target frequency
count_target(df_targets)

# Plot target frequency
plot_target_count(df_targets)
```

Furthermore, miRNA-target interactions can be plotted with `plot_target_mir_scatter()`.  
`plot_target_mir_scatter()` plots either the most frequently targeted
genes, or it plots the top miRNAs targeting genes. If the focus shall be on the top targets
or top targeting miRNAs, can be regulated via the `filter_for` argument.

```{r, eval = FALSE}
# Plot most frequently targeted genes
plot_target_mir_scatter(df_targets,
                        filter_for = "target")

# Plot most frequently targeting miRNAs
plot_target_mir_scatter(df_targets,
                        filter_for = "miRNA")
```

### Single Nucleotide Polymorphism

Single Nucleotide Polymorphisms (SNPs) can be extracted from abstracts with
`extract_snp()`.  

`extract_snp()` retrieves SNPs from abstracts
and stores them in a column. Unlike `extract_mir_df()`, however, all
extracted SNPs of an abstract are stored in the same row. Furthermore, `extract_snp()` 
can also subset abstracts containing SNPs via the `discard` argument.

```{r, eval = FALSE}
# Exctract SNPs
# Keep only abstracts with SNPs
snp_df <- extract_snp(df,
                      discard = TRUE)
```

Extracted SNPs can be counted with `count_snp()`, while abstracts can be subset 
for specific SNPs with `subset_snp()`.  
To facilitate filtering for SNPs, SNP names can be extracted from 
a data frame with `get_snp()`. `get_snp()` retrieves the string of a SNP
by row, which can be passed to `subset_snp()`.

```{r, eval = FALSE}
# Count SNPs
snp_count_df <- count_snp(snp_df)

# Extract SNP name in the second row of snp_count_df
second_snp_string <- get_snp(snp_count_df,
                             row = 2)

# Subset `snp_df` for abstracts containing `second_snp_string`
subset_snp(snp_df,
           snp.retain = second_snp_string)
```

## miRNA text mining in multiple subjects

Next to miRNA text mining in a single subject, miRetrieve also 
offers tools to compare the results of miRNA text mining in multiple subjects.  

In this section, we are going to explain how to compare miRNA count and
miRNA-term association. Furthermore, we are going to describe how to visualize 
miRNA-target interactions across fields.

### Data preparation

To compare different subjects, each subject is loaded separately with `read_pubmed_*()`.
Furthermore, each field must be assigned a distinct topic name, using either
the `topic` argument of `read_pubmed_*()` or `add_col_topic()`. Afterwards, all files 
are combined for further analysis with `combine_df()`.

```{r, eval = FALSE}
# Load abstracts of the first topic
df1 <- read_pubmed_medline(medline_file1, topic = "Virus")

# Load abstracts of the second topic
df2 <- read_pubmed_medline(medline_file2, topic = "Bacteria")

# Combine abstracts of topics
df_combined <- combine_df(df1, df2)
```

### Extract miRNA names as strings

A key difference to text mining in one subject is that the miRNAs to analyze 
must be specified.  

For this, miRNA names can be extracted as strings from a
data frame using `get_mir()`, `get_shared_mir*()`, `get_distinct_mir_*()`, 
and `combine_mir()`.  

* `get_mir()` extracts either the most frequently mentioned
miRNAs or the miRNAs that are mentioned in a minimum number of abstracts.  
Moreover, `get_mir()` can also extract the top miRNAs of one subject with a 
`topic` argument.

    ```{r, eval=FALSE}
    # Get top 5 miRNAs of all topics
    get_mir(df_combined,
            top = 5)
    
    # Get top 5 miRNAs of the topic "Atherosclerosis"
    get_mir(df_combined,
            top = 5,
            topic = "Atherosclerosis")
    ```

* `get_shared_mir*()` provides the most frequent miRNAs that are shared 
between two subjects. `get_shared_mir_df()` extracts the shared miRNAs 
from a data frame, while `get_shared_mir_vec()` extracts the shared miRNAs
from two character vectors.

    ```{r, eval=FALSE}
    # Get top shared miRNAs of "T1DM" and "T2DM"
    get_shared_mir_df(df_combined,
                      topic = c("T1DM", "T2DM"))
    ```

* `get_distinct_mir*()` provides the most frequent miRNAs that are distinct 
for one topic, but do not belong to the top miRNAs of another topic.
`get_distinct_mir_df()` extracts the distinct miRNAs from a data frame, while
the topic to extract the distinct miRNAs from is determined with the `distinct`
argument.  
`get_distinct_mir_vec()` extracts the distinct miRNAs of the first
character vector from two character vectors.

    ```{r, eval=FALSE}
    # Get top miRNAs distinct for "ALL" compared to "AML"
    get_distinct_mir_df(df_combined, 
                        distinct = "ALL",
                        topic = c("ALL", "AML"))
    ```

* `combine_mir()` combines character vectors with miRNA names into one vector. 

    ```{r, eval=FALSE}
    # Get top 5 miRNAs of "CML"
    top_topic1 <- get_mir(df_combined,
                          top = 5,
                          topic = "CML")
    
    # Get top 5 miRNAs of "CLL"
    top_topic2 <- get_mir(df_combined,
                          top = 5,
                          topic = "CLL")
    
    # Combine vectors
    top_combined <- combine_mir(top_topic1, top_topic2)
    ```

### Compare miRNA count

How many abstracts per subject mention a miRNA can be compared with `compare_mir_count()`.  

`compare_mir_count()` can display either the absolute number of abstracts per subject mentioning
a miRNA, or it can display the relative number of abstracts per subject
mentioning a miRNA, referring to the number of abstracts with a miRNA relative to 
all abstracts per subject.  
Furthermore, the relative count of miRNAs can be comperd between two subjects on a 
log2-scale with `compare_mir_count_log2()`.

```{r, eval = FALSE}
# Use `top_combined` from the previous code chunk

# Compare miRNA frequency between topics
compare_mir_count(df_combined,
                  mir = top_combined)

# Compare miRNA frequency between subjects on a log2-scale
compare_mir_count_log2(df_combined,
                       mir = top_combined)
```

### Compare term associations

There are three functions to compare miRNA-term associations across subjects,
namely `compare_mir_terms()`, `compare_mir_terms_log2()`, and `compare_mir_terms_scatter()`.

While `compare_mir_terms()` can compare the top term count of a miRNA over many subjects,
`compare_mir_terms_log2()` and `compare_mir_terms_scatter()` can compare the top 
term count of a miRNA over two subjects only.

`compare_mir_terms()` plots the count of top miRNA-term associations, whereas   
`compare_mir_terms_log2()` compares the miRNA-term association between two subjects 
on a log2-scale.^[The plot created by `compare_mir_terms_log2()`
is greatly inspired by *Text Mining with R* by Silge and Robinson[@tidytext].]

```{r, eval = FALSE}
# Compare term frequency for miR-126 between topics
compare_mir_terms(df_combined,
                  mir = "miR-126")

# Compare term frequency for miR-126 between two topics on a log2-scale
compare_mir_terms_log2(df_combined,
                       mir = "miR-126")
```

Finally, `compare_mir_terms_scatter()` compares the top miRNA-term associations
in two ways:

First, `compare_mir_terms_scatter()` creates a scatter plot, displaying the
frequency of the shared miRNA-associated terms.^[The plot generated by
`compare_mir_terms_scatter()` is greatly inspired by *Text Mining with R* by Silge and Robinson[@tidytext].]

Second, `compare_mir_terms_scatter()` creates one data frame per subject, containing 
unique miRNA-term associations for each subject.

`compare_mir_terms_scatter()` returns the scatter plot and the data frames in a
list. Within the list, the scatter plot can be accessed with `$scatter`, while
the data frame of the two subjects can be accessed with `$unique_topic_one` and
`$unique_topic_two` respectively.

```{r, eval=FALSE}
# Compare terms of miR-126 between two topics
mir126_terms <- compare_mir_terms_scatter(df_combined,
                                          mir = "miR-126")

# Compare common terms of miR-126 as a scatter plot
mir126_terms$scatter

# Terms unique of miR-126 for the first topic
mir126_terms$unique_topic_one

# Terms unique of miR-126 for the second topic
mir126_terms$unique_topic_two
```

### Compare target interactions

As described previously, targets can be added from an excel file with `join_targets()`. 
When a data frame contains miRNA-target interactions in multiple subjects, 
`plot_target_mir_scatter()` colours the miRNA-target interaction by subject, 
thereby allowing easy comparison of miRNA-target interactions across fields.

# Case study

In the last section, we are going to apply miRetrieve in a small case study.   

## Introduction

In this fictive case study, our lab detected miR-21 to be aberrantly expressed in colorectal 
cancer (CRC).
Using miRetrieve, we characterize the role of miR-21 in CRC and compare it
to its role in pancreatic cancer.  

## Data preparation

To investigate the role of miR-21 in CRC, we load all PubMed abstracts matching 
the keywords *colorectal cancer mirna* with `read_pubmed_medline()`. Then, 
we keep only abstracts of original research articles, using `subset_research()`, and 
subsequently extract their miRNA names with `extract_mir_df()`.  

During our analysis, we use the `%>%` operator from the **magrittr** package. 
`%>%` passes the result of one function straight into
the following function, making our code easier to write, read, and maintain.

```{r}
# Load miRetrieve
library(miRetrieve)
# Load magrittr
library(magrittr)

# Path to MEDLINE-file
crc_medline <- "CRC_Medline.txt"

# Load MEDLINE-file
df_crc <- read_pubmed_medline(crc_medline,
                              topic = "CRC") %>%
  # Keep abstracts of original research articles
  subset_research() %>% 
  # Extract miRNA names
  extract_mir_df() 
```

After loading and filtering the abstracts, we have a data frame with
`r nrow(df_crc)` rows and `r ncol (df_crc)` columns, named
*`r colnames(df_crc)`*. As each miRNA name occupies one row in the `miRNA` column,
and each abstract can mention more than one miRNA, there are more rows
in the data frame than abstracts under investigation.

## Indicate miR-21 in CRC and save file

We know that we are going to need information on miR-21 in the future. 
We therefore label all abstracts mentioning miR-21 with 
`indicate_mir()`, and save the table as an .xlsx-file. 
Saving the table locally will allow us to read and compare PubMed 
abstracts mentioning miR-21 comfortably.

```{r, eval=FALSE}
# Label all abstracts mentioning miR-21 with "Yes"
df_mir21 <- indicate_mir(df_crc,
                         indicate.mir = "miR-21")

# Save as an .xlsx file
save_excel(df_mir21,
           excel_file = "miR21_crc.xlsx")
```

## Count miRNAs in CRC

To begin our analysis, we count the top miRNAs in CRC using `plot_mir_count()`. 
If miR-21 should not be among the top miRNAs, we plan on counting all miRNAs with 
`count_mir()`, filter the resulting data frame for miR-21 with `subset_df()`, and 
distinctively determine the count of miR-21.

```{r,fig.show='hold', out.width='50%', fig.align='center'}
# Plot count of top miRNAs in CRC
plot_mir_count(df_crc)
```

In CRC, miR-21 seems to be the most frequently mentioned miRNA, being
reported in more than 250 abstracts. Next to miR-21, miR-145, miR-200, and miR-34 
are also mentioned frequently in CRC.

## Plot miR-21 associated terms in CRC

As miR-21 is likely well investigated in CRC, we identify which terms miR-21 
is associated with using `plot_mir_terms()`.  

To analyze the terms miR-21 is associated with, we choose to tokenize the text into 
single words and into 2-grams:  

For single word tokenization, we remove English and PubMed stop words 
by combining `tidytext::stop_words` and `miretrieve_stopwords` with `combine_stopwords`, before
feeding the resulting data frame to `plot_mir_terms()`.  

For 2-gram tokenization, we remove English stop words by setting 
`stopwords_ngram = TRUE`.

```{r, fig.show='hold', out.width='50%'}
# Combine tidytext::stop_words and stopwords_miretrieve
stopwords_com <- combine_stopwords(tidytext::stop_words,
                                   stopwords_miretrieve)

# Plot top single terms associated with miR-21 in CRC
plot_mir_terms(df_crc,
               "miR-21",
               stopwords = stopwords_com,
               top = 30)

# Plot top 2-grams associated with miR-21 in CRC
plot_mir_terms(df_crc,
               "miR-21",
               token = "ngrams",
               n = 2,
               stopwords_ngram = TRUE)
```

The top single terms for miR-21 suggest that miR-21 is associated with *survival*, 
even though *survival* is most likely a word common in cancer literature. 
Furthermore, it is implied that miR-21 targets *PTEN* and *PDCD4*. 
As miR-21 is also often associated with *serum*, *plasma*, and *biomarker*, miR-21 might 
be a biomarker.  

The 2-gram tokenization implies that miR-21 is frequently mentioned
with miR-145, miR-17, miR-31, and miR-20a, which hints at possible miR-miR interactions 
and co-regulations.

## miRNAs as biomarkers in CRC

As miR-21 might be a biomarker in CRC, we determine the most frequently 
mentioned miRNAs in biomarker abstracts.  

Here, we first subset for biomarker abstracts with `calculate_score_biomarker()`
and setting `discard = TRUE`.  
As `calculate_score_biomarker()` requires a threshold to distinguish abstracts
with and without biomarker, we try to determine a reliable threshold using 
`plot_score_biomarker()`.

```{r,fig.show='hold', out.width='50%', fig.align='center'}
# Plot score distribution for biomarker in CRC
plot_score_biomarker(df_crc)
```

While the majority of abstracts do not seem to report miRNAs as biomarkers in CRC, 
using a threshold above 5 in `calculate_score_biomarker()` seems reasonable.
After identifying abstracts describing biomarkers, we count the top miRNAs with 
`plot_mir_count()`.

```{r,fig.show='hold', out.width='50%', fig.align='center'}
# Identify abstracts reporting miRNAs as biomarker in CRC
crc_biomarker <- calculate_score_biomarker(df_crc,
                                           threshold = 5,
                                           discard = TRUE)

# Plot top potential biomarker miRNAs in CRC
plot_mir_count(crc_biomarker)
```

miR-21 is mentioned in more than 50 abstracts potentially reporting biomarkers,
and thus very likely to be a biomarker in CRC.

## miRNAs as biomarkers in pancreatic cancer

To determine if miR-21 is a specific biomarker for CRC, 
we compare it to possible miRNA biomarkers in another cancer entity, 
namely pancreatic cancer.  

First, we load abstracts matching the keywords *pancreatic cancer mirna*, 
keep only abstracts of original research articles, and extract their miRNA names.
Next, we identify the top possible biomarker miRNAs with `plot_score_biomarker()`, `calculate_score_biomarker()`, and `plot_mir_count`. If miR-21 is not among the
top biomarker miRNAs in pancreatic cancer, we subset all biomarker abstracts for miR-21
with `subset_df()` and count miR-21 selectively with `count_mir()`.

```{r, fig.show='hold', out.width='50%'}
# Path to MEDLINE-file
panc_medline <- "Pancreas_Medline.txt"

# Load MEDLINE-file
df_panc <- read_pubmed_medline(panc_medline,
                              topic = "Pancreas") %>% 
  # Keep original research articles
  subset_research() %>% 
  # Extract miRNA names
  extract_mir_df()

# Plot score distribution for biomarker in pancreatic cancer
plot_score_biomarker(df_panc)

# Identify abstracts reporting miRNAs as biomarker in pancreatic cancer
panc_biomarker <- calculate_score_biomarker(df_panc,
                                           threshold = 6,
                                           indicate = TRUE,
                                           discard = TRUE)

# Plot top potential biomarker miRNAs in pancreatic cancer
plot_mir_count(panc_biomarker)
```

miR-21 is mentioned in about 35 abstracts reporting miRNAs as biomarkers in pancreatic
cancer. This suggests that miR-21 is most likely a biomarker in pancreatic cancer, but
hence no biomarker specific for either CRC or pancreatic cancer.

## Target interactions of miR-21 in CRC and pancreatic cancer

As miR-21 seems to be a biomarker in CRC and pancreatic, we determine
if miR-21 also shares miRNA-target interactions in both tumor entities.  

First, we combine the CRC and pancreatic cancer data frames with `combine_df()`. 
Next, we look up the experimentally validated targets by adding the *miRTarBase*[@mirtarbase] 
database with `join_targets()`. Finally, we keep only the targets of miR-21 with `subset_mir()` 
and plot them with `plot_target_mir_scatter()`.

```{r,fig.show='hold', out.width='50%', fig.align='center'}
# Combine CRC and pancreatic cancer data frames
df_crc_panc <- combine_df(df_crc, df_panc)

# Path to miRTarBase (see "References")
target_db <- "miRTarBase_MTI.xlsx"

# Add miRTarBase targets to `df_crc_panc`
df_targets <- join_targets(df_crc_panc, target_db,
                           col.pmid.excel = "References (PMID)",
                           col.target.excel = "Target Gene",
                           col.mir.excel = "miRNA",
                           stem_mir_excel = TRUE)

# Subset for miR-21
df_targets_mir_21 <- subset_mir(df_targets,
                                mir.retain = "miR-21",
                                col.mir = miRNA_excel)

# Plot top targets for miR-21 in CRC and pancreatic cancer
plot_target_mir_scatter(df_targets_mir_21,
                        col.mir = miRNA_excel,
                        top = 10,
                        filter_for = "target")
```

According to *miRTarBase*, miR-21 shares at least three targets across CRC and 
pancreatic cancer, namely *PDCD4*, *PTEN*, and *RPS7*. However, miR-21 is also
known to target only specific genes in one subject so far, such as *RASA1*, *SPRY2*, 
or *TIAM1* in CRC, or *BCL2*, *FASLG*, *HIF1A*, *MMP2*, or *MMP9* in pancreatic cancer.  

For our project, it is therefore interesting to investigate if miR-21 
regulates also one of the uniquely in pancreatic cancer reported targets 
in CRC.

## Top miRNA-target interactions in CRC and pancreatic cancer

Lastly, we identify the three genes that are targeted by most miRNAs in CRC
and pancreatic cancer with `plot_mir_scatter()`.

```{r,fig.show='hold', out.width='50%', fig.align='center'}
# Plot top 3 miRNA targets in CRC and pancreatic cancer
plot_target_mir_scatter(df_targets,
                        col.mir = miRNA_excel,
                        top = 3,
                        filter_for = "target")
```

According to *miRTarBase*, *PTEN*, *SMAD4*, and *TGFBR2* are the most targeted
genes in CRC and pancreatic cancer. As more miRNAs have been validated to 
regulate *PTEN*, *SMAD4*, and *TGFBR2* in CRC than in pancreatic cancer, an interesting
next step would be to investigate if the same mechanisms also take place in 
pancreatic cancer.

## Conclusion

With few lines of code, we determined that miR-21 is a frequently mentioned 
and thus most likely well investigated miRNA in CRC. Furthermore, we revealed 
that miR-21 is possibly a non-specific biomarker for CRC and pancreatic cancer.
Next to that, we gained insight into common and distinct targets of
miR-21 in both diseases, while also observing that *PTEN*, *SMAD4*, and
*TGFBR2* are targeted by multiple miRNAs in both fields.  

While the mention of a miRNA and the terms it is associated with in an abstract 
need to be interpreted carefully, text mining miRNAs with miRetrieve provides the 
opportunity to generate and test hypotheses on the fly, which can serve as 
a starting point for subsequent research.

# References
